---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# vicbabynames

<!-- badges: start -->
<!-- badges: end -->

This is a wrapper to the Victorian Government Popular Baby Names API. See https://wovg-community.portal.prod.api.vic.gov.au/api-catalogue

This is just a test, but the package works.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("williamlai2/vicbabynames")
```
## Example

If you don't have an API Key, you can get one for free from https://wovg-community.portal.prod.api.vic.gov.au/

```{r}
library(vicbabynames)

# set your api key - this is just the sample available from the Vic Gov website.
#set_api_key()
```

It is probably better to `get_all_data()` then filter using `dplyr` later.

```{r}
get_all_data()
```

But you can filter by a year if you want. Data is available from 2008 onwards.

```{r}
get_year_data(2008)
```
